DIAGNOSTIC SUPPORT OF SKIN LESION CLASSIFICATION USING CNN AND SOFT ATTENTION

### 2022-06-29 MDPI/Sensor Paper/template.tex
Update Ver 4 MDPI Sensor Paper

In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models wich have been used as a backbone model in this paper will be discussed in the Related Work section.

@@

Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}. The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al. 
\begin{table}[ht]
	\centering
	\begin{tabular}{|c c c c c c c c c|} 
		\hline
		Class & AKIEC & BCC & BKL & DF & MEL & NV & VASC & Total \\ 
		\hline
		No. Sample & 327 & 514 & 1099 & 115 & 1113 & 6705 & 142 & 10015 \\
		\hline
	\end{tabular}
	\caption{Data Distribution in HAM10000}
	\label{table:1}
\end{table}

>>>>

In order to adapt the rise in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models which have been used as a backbone model in this paper will be discussed in the Related Work section.

@@

Otherwise, the Student and Teacher Model is also a state of the art in 2021\cite{03225}. The student and teacher model is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. SkinLinkNet\cite{12602} and WonderM\cite{03426} are both tested the effect of segmentation on skin lesion classification problem created by Amirreza et al and Yeong Chan et al, respectively. In WonderM, the method used is padding the image so that the image has the shape increased from (450,600) to (600, 600). In SkinLinkNet, instead resize the image down to (448, 448). Both of SkinLinkNet and WonderM use UNet to do the segmentation task, though they use EfficientNetB0 and DenseNet to do the classification task, respectively. Another approach is using metadata including gender, age, and capturing position as stated in \cite{03910} by Nil Gessert et al.

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \cite{03798} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in\cite{10348} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \cite{05045} by Michele Alberti et al. 
\begin{table}[ht]
	\centering
	\begin{tabular}{|p{1cm}|p{12.5cm}|}
		\hline
		Work & Approach \\ 
		\hline
		\cite{03358} & Combination of Backbone Model and Soft Attention. Backbone model includes DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34\\
		\hline
		\cite{03798} & Transfer Learning with CNN based model\\
		\hline
		\cite{10348} & Transfer Learning with CNN based model including DenseNet201, InceptionResNetV2, VGG16, ResNet50, ResNet34, and InceptionNetV3\\
		\hline
		\cite{09418} & Transfer Learning with CNN based model including EfficientNet and SeNet. Data augmentation process used CutOut to create random sized hole considered as an inactive portion of image.\\
		\hline
		\cite{01284} & Transfer Learning with CNN based model. Data augmentation process uses RandArgument to split picture into several pictures which is used to train. DropBlock and Multi-Weight Loss Function are used to deal with the imbalanced.\\
		\hline
		\cite{06612} & GradCam and Kernel SHAP, two model agnostic, local interpretable methods that can highlight pixels that the trained network deems relevant for the final classification.\\
		\hline
		\cite{03225} & Student and Teacher Model is the combination of two model which share the memory learned with others. \\
		\hline
		\cite{12602} & SkinLinkNet uses the image whose shape is (448,488) for training. Unet and EfficientNetB0 are used for segmentation and classification task respectively.\\
		\hline
		\cite{03426} & WonderM uses the image whose shape is (600,600) created by padding for training. Unet and DenseNet are used for segmentation and classification task respectively.\\
		\hline
		\cite{03910} & MetaData including age, gender, and capture position are used to gain higher performance of the model. The models used in this paper are CNN-based model \\
		\hline
		\cite{03798} & Traditional Machine Learning Algorithms are applied including Random Forest, XGBoost, and Support Vector Machine \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function \\
		\hline
		\cite{05045} & Isolation Forest are applied distribution skin lesion images before fedding into the softmax activation function. \\
		\hline
		\cite{10348} & Matrix Factorization are applied before the softmax activation function. \\
		\hline
	\end{tabular}
	\caption{Related Works Summary}
	\label{table:0}
\end{table}
